A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
add case study outline

>>>>

\begin{itemize}
\item Escape Hatch: \c{eval(unlock_binding ... )} to prevent R CMD check warnings
\item Accessing data frame columns like local variables: \c{eval(x + y + z, data.frame(x, y z))}
\item Poor man's sandboxing: local function
\item Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
\item Convenience: 
\item Dynamic code loading: \c{eval(parse(...))}. The textual input in parse can come from three places: a string, a file or in interactive R sessions directly from user input. Next to \c{parse}, there are also \c{str2expression} and \c{str2lang} which are a specialized versions of parse that do not keep source references and thus are a bit faster.
\item bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
\item evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.
\end{itemize}
